Entrainment of low Mach number thermals in stratified domains

### 2019-05-10 tex/stratified_thermals.tex
a little wordsmithing

@@

\subsection{Evolution of momentum and impulse}
The evolution of thermals as buoyant vortex rings has been well described in
the unstratified, Boussinesq limit for decades (as early as e.g., CITE, and
see \citet{lecoanet&jeevanjee2018} for other sources). Buoyant motions 
in the atmospheres of stars and planets are generally large enough to feel the
atmospheric stratification, and therefore a more thorough treatment of the
evolution of thermals in stratified domains is required to understand 
thermal entrainment in nature. We will use a description of the momentum and
impulse acting on the thermal to develop a theory of depth of thermals as a function
of time, as well as the growth of their radii with depth.

>>>>

In the following sections, we will use a description of the impulse and momentum of these
thermals, as determined by their buoyant nature, to describe the evolution of their depth
and radii with time.

@@

\subsection{Evolution of momentum and impulse}
The evolution of thermals as buoyant vortex rings has been well described in
the unstratified, Boussinesq limit for decades 
\citep[see e.g.][for a description and sources]{lecoanet&jeevanjee2018}.
Here we lay out a description of the momentum and
impulse of the thermal which will later be used 
to describe thermal properties like radii and depth vs. time.
